Predicting sales of newly published books

### 2015-09-10 paper.tex
Entering the "problem description"
With lots of material to move or eliminate.

The main issue of this paper is to forecast sales for 
unpublished books for which no historical data is available, just some
descriptive variables relative to the new book. In order to do that,
training data includes historical sales data for all books published
in Spain for several years, including those descriptive variables.

%Después de esto no sé si merece la pena dejar este párrafo.
Forecasting sales of new books is a problem with issues 
such as dealing with limited data, finding adequate forecasting methods and 
selecting the best method to use \cite{ChingChin2010}. % He cambiado
                                % esto, pero sigue sin decir
                                % absolutamente nada. "The problem"
                                % tiene que describir el problema: qué
                                % queremos hacer, qué tenemos - JJ

In the case of already published books, available historical data might help 
to generate predictive models.
However, in the case of new books there is no historical data to define patterns, 
and only some descriptive data about the new book is available. 
%FERGU: data es plural. is->are   ...a mí me suena bien con "is"   ¡una segunda opinión!   ;)
In these cases not any forecasting method can be used \cite{Madsen2008,ChernWSF15}.

An additional issue is the difficulty to compare our model with classical 
forecasting methods, such as time series prediction methods, since books 
do not have specific sales time series.

Throughout this research, we collaborated with the company Trevenque Editorial, %\footnote{{\tt http://editorial.trevenque.es}}, 
a company that provides management systems and services for libraries, publishers 
and distributors.

Trevenque company, whose expert manager advised this research, provided %FERGU: los párrafos anteriores son un poco dispersos, puedes quitar los puntos y aparte y agruparlos por temas (por ejemplo, todo lo de Trevenque debería de ir en un párrafo)
the initial data set consisting of 3159 books.
In this data set, descriptive information for each book includes price, 
selling points, subject, publisher, sales, returns, among other information.
Table \ref{tabla:paramsOrig50} shows the original set of parameters describing 
each book.

>>>>

The main issue of this paper is to forecast sales for 
unpublished books for which no historical data is available, just some
descriptive variables relative to the new book. In order to do that,
training data includes historical sales data for all books published
in Spain for several years, including those descriptive variables. 
%
%%% Principio de párrafos a eliminar o mover a estado del arte.
%Después de esto no sé si merece la pena dejar este párrafo.
Forecasting sales of new books is a problem with issues 
such as dealing with limited data, finding adequate forecasting methods and 
selecting the best method to use \cite{ChingChin2010}. % He cambiado
                                % esto, pero sigue sin decir
                                % absolutamente nada. "The problem"
                                % tiene que describir el problema: qué
                                % queremos hacer, qué tenemos - JJ

% Este párrafo o se borra o se traslada al estado del arte. Aquí hay
% que contar cuál es el problema y qué se tiene. No se puede volver a
% repetir lo de antes.
In the case of already published books, available historical data might help 
to generate predictive models.
However, in the case of new books there is no historical data to define patterns, 
and only some descriptive data about the new book is available. 
%FERGU: data es plural. is->are   ...a mí me suena bien con "is"   ¡una segunda opinión!   ;)
In these cases not any forecasting method can be used \cite{Madsen2008,ChernWSF15}.

% Vale, más issues. Este párrafo también puede quedar fuera. Ya has
% dicho que no se puede usar la serie histórica.
An additional issue is the difficulty to compare our model with classical 
forecasting methods, such as time series prediction methods, since books 
do not have specific sales time series.

Throughout this research, we collaborated with the company Trevenque Editorial, %\footnote{{\tt http://editorial.trevenque.es}}, 
a company that provides management systems and services for libraries, publishers 
and distributors. % Esto tampoco viene a cuento. Se dice en la intro o
                  % se cuenta como gente que nos ha proporcionado los
                  % datos y nos contrató para hacerlo.

Trevenque company, whose expert manager advised this research,
provided %FERGU: los párrafos anteriores son un poco dispersos, puedes
         %quitar los puntos y aparte y agruparlos por temas (por
         %ejemplo, todo lo de Trevenque debería de ir en un párrafo) 
% O borrarlos - JJ
%% Fin de párrafos a eliminar.
This initial data set, provided in the framework of a contract by
Trevenque Editorial, included 3159 books, and included descriptive information for each book includes price, 
points of sale, subject, publisher, sales, returns, among other information.
Table \ref{tabla:paramsOrig50} shows the original set of parameters describing 
each book.
